Paper 1 Notebook

### 2023-11-30 minos/outcomes/paper_1_notebook.Rmd
slight adjustments to mice in plots

load_cache <- F
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  n_iter <- 30
  max_iter <- 10
  # future mice is parallelised version of MICE.
  mice_set <- futuremice(data = mice.data, #method=method,
                   #m = 10, maxit = 30,
                   m = n_iter, maxit = max_iter,
                   remove.collinear=F)
  saveRDS(mice_set, "data/transitions/MICE_set.rds")
}

@@

# coefficient forest plot. 
forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))

>>>>

load_cache <- F
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  n_iter <- 20
  max_iter <- 5
  # future mice is parallelised version of MICE.
  mice_set <- futuremice(data = mice.data, #method=method,
                   #m = 10, maxit = 30,
                   m = n_iter, maxit = max_iter,
                   remove.collinear=T)
  saveRDS(mice_set, "data/transitions/MICE_set.rds")
}

@@

# coefficient forest plot. 
forest_plot(mice.lm.object, paste0(save.path,'mice_SF12_forest.pdf'))
qq_plot(resid(mice.lm.object), paste0(save.path, "mice_qq.pdf"))
